### 2017-03-21 doc/manuscript.Rmd
Fix pls figure dimensions

```{r fig_pls, fig.cap=fig_pls}
gridExtra::grid.arrange(
    plot_pls(pls_homa2) + ggplot2::ggtitle('A: HOMA2-%S'), 
    plot_pls(pls_isi) + ggplot2::ggtitle('B: ISI'), 
    ncol = 2)
```

>>>>

```{r fig_pls, fig.cap=fig_pls, fig.height=8, fig.width=4}
gridExtra::grid.arrange(
    plot_pls(pls_homa2) + ggplot2::ggtitle('A: HOMA2-%S'), 
    plot_pls(pls_isi) + ggplot2::ggtitle('B: ISI'), 
    ncol = 1)
```
